HO unification from object language to meta language

### 2024-02-23 paper/main.tex
c -> con

\begin{elpicode}
type lam  tm -> (tm -> tm) -> tm.     % lambda abstraction
type app  list tm -> tm.              % n-ary application
type all  tm -> (tm -> tm) -> tm.     % forall quantifier
type c    string -> tm.               % constants
\end{elpicode}

@@

\begin{elpicode}
all (c"t") y\ app[c"nfact", y, c"3"]
\end{elpicode}

@@

\begin{elpicode}
finite (app[c"fin", N]).                              ~\customlabel{clause:r1}{(r1)}~
decision (app [c"nfact", N, NF]).                     ~\customlabel{clause:r2}{(r2)}~
decision (all A x\ app[P, x]) :- finite A,            ~\customlabel{clause:r3}{(r3)}~
  pi w\ decision (app[P, w]).
\end{elpicode}

@@

\begin{elpicode}
decision (all (app[c"fin", c"7"]) y\                 
  app[c"nfact", y, c"3"]).
\end{elpicode}

@@

\begin{elpicode}
app[c"nfact", y, c"3"] = app[P, y]                     ~\customlabel{problem:p}{(p)}~
\end{elpicode}

@@

\begin{elpicode}
app[c"nfact", y, c"3"] = Pm y                         ~\customlabel{problem:pa}{(pa)}~
Pm = x\ app[c"nfact", x, c"3"]       % assignment for Pm
A = app[c"fin", c"7"]                % assignment for A
\end{elpicode}

@@

\begin{elpicode}
P = lam A a\ app[c"nfact", a, c"3"]
\end{elpicode}

@@

\begin{elpicode}
decision (app[lam A (a\ app[c"nfact", a, c"3"]), w])
\end{elpicode}

@@

\begin{elpicode}
app[lam A (a\ app[c"nfact", a, c"3"]), x] =
  app[c"nfact", N, NF]
\end{elpicode}

@@

\begin{tabular}{lcl}
\elpiIn{x\ f x} & \Ue{} & \elpiIn{f}\\
\elpiIn{lam A x\ app[c"f", x]} & \Uo{} & \elpiIn{c"f"}\\
\elpiIn{lam A x\ app[c"f", x]} & \nUe{} & \elpiIn{c"f"} \\
\elpiIn{P x} & \Ue{} & \elpiIn{x}\\
\elpiIn{app[P, x]} & \Uo{} & \elpiIn{x}\\
\elpiIn{app[P, x]} & \nUe{} & \elpiIn{x}\\
\end{tabular}

>>>>

\begin{elpicode}
type lam  tm -> (tm -> tm) -> tm.     % lambda abstraction
type app  list tm -> tm.              % n-ary application
type all  tm -> (tm -> tm) -> tm.     % forall quantifier
type con  string -> tm.               % constants
\end{elpicode}

@@

\begin{elpicode}
all (con"t") y\ app[con"nfact", y, con"3"]
\end{elpicode}

@@

\begin{elpicode}
finite (app[con"fin", N]).                            ~\customlabel{clause:r1}{(r1)}~
decision (app [con"nfact", N, NF]).                   ~\customlabel{clause:r2}{(r2)}~
decision (all A x\ app[P, x]) :- finite A,            ~\customlabel{clause:r3}{(r3)}~
  pi w\ decision (app[P, w]).
\end{elpicode}

@@

\begin{elpicode}
decision (all (app[con"fin", con"7"]) y\                 
  app[con"nfact", y, con"3"]).
\end{elpicode}

@@

\begin{elpicode}
app[con"nfact", y, con"3"] = app[P, y]                 ~\customlabel{problem:p}{(p)}~
\end{elpicode}

@@

\begin{elpicode}
app[con"nfact", y, con"3"] = Pm y                     ~\customlabel{problem:pa}{(pa)}~
Pm = x\ app[con"nfact", x, con"3"]     % assignment for Pm
A = app[con"fin", con"7"]              % assignment for A
\end{elpicode}

@@

\begin{elpicode}
P = lam A a\ app[con"nfact", a, con"3"]
\end{elpicode}

@@

\begin{elpicode}
decision (app[lam A (a\ app[con"nfact", a, con"3"]), w])
\end{elpicode}

@@

\begin{elpicode}
app[lam A (a\ app[con"nfact", a, con"3"]), x] =
  app[con"nfact", N, NF]
\end{elpicode}

@@

\begin{tabular}{lcl}
\elpiIn{x\ f x} & \Ue{} & \elpiIn{f}\\
\elpiIn{lam A x\ app[con"f", x]} & \Uo{} & \elpiIn{con"f"}\\
\elpiIn{lam A x\ app[con"f", x]} & \nUe{} & \elpiIn{con"f"} \\
\elpiIn{P x} & \Ue{} & \elpiIn{x}\\
\elpiIn{app[P, x]} & \Uo{} & \elpiIn{x}\\
\elpiIn{app[P, x]} & \nUe{} & \elpiIn{x}\\
\end{tabular}
